Incentivizing Exploration with Unbiased History

### 2018-11-02 3level.tex
fix 3level

\jmcomment{$N_2$ is also used in Lemma 3.6. We need to find another notation. And I think it should be something without subscript 2. It's generally a property of the whole construction. How about $\NG$.}

@@

\begin{lemma}[Large gap]\label{3levelbigcase}
If
% $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
%  \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$,
  $ \Delta \geq 4 \sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$
then all agents in Levels 2 and 3 pull arm 1.
\end{lemma}

In the \emph{medium gap} case, the data collected in a given first-level group is no longer guaranteed to determine the best arm. However, the data collected by the second-level groups enables all agents in the third level to correctly identify the best arm.

@@

Finally, the \emph{small gap} case, when  $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(\NG\, T_1)})$
is more challenging since even aggregating the data from all $\NG$
first-level groups is not sufficient for identify the best arm.
We need to ensure that both arms continue to be explored in the second level.
To achieve this, we leverage \event{4}, which implies
that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the agents' reward estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
from this group $s_a$ ensures that all agents in the respective second-level group prefer arm $a$. Therefore, both arms are pulled at least $T_2$ times in the second level, which in turn gives the following guarantee:

>>>>

%\jmcomment{$N_2$ is also used in Lemma 3.6. We need to find another notation. And I think it should be something without subscript 2. It's generally a property of the whole construction. How about $\NG$.}

@@

\begin{lemma}[Large gap]\label{3levelbigcase}
If
% $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
%  \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$,
  $ \Delta \geq 4 \sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$
then all agents in the second and the third levels pull arm 1.
\end{lemma}

In the \emph{medium gap} case, the data collected in a given first-level group is no longer guaranteed to determine the best arm. However, agents in the third level see the history of not only one but all first-level groups and the data collected by all first-level groups enables agents in the third level to correctly identify the best arm.

@@

Finally, the \emph{small gap} case, when  $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(\NG\, T_1)})$
is more challenging since even aggregating the data from all $\NG$
first-level groups is not sufficient for identifying the best arm.
We need to ensure that both arms continue to be explored in the second level.
To achieve this, we leverage \event{4}, which implies
that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the agents' reward estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
from this group $s_a$ ensures that all agents in the respective second-level group prefer arm $a$. Therefore, both arms are pulled at least $T_2$ times in the second level, which in turn gives the following guarantee:
